A holomorphic approach to branes in twisted~$M$-theory

### 2022-08-22 fivebranes/twisted.tex
update

The interacting part of the action is more complicated, partly for the reason that in our presentation above it is given by a formal series in the space of fields, rather than just a polynomial in the fields. 
Explicitly, the interaction can be written as
\beqn
\label{eqn:int}
\frac12 \int_{S \times X} (\mu^2 \del \gamma) \frac{\Omega_X}{1- \nu} + \frac16 \int_{S \times X} \gamma \del \gamma \del \gamma .
\eeqn
%
%Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.

@@

\brian{non BV setup}

@@

We briefly recall the description of the minimal twist of the ABJM theory associated to the single membrane theory.
Let $K^{1/4}_C$ be a fourth-root of the canonical bundle of $C$. 
In the BV formalism, this free theory has underlying space of fields
\[
\Omega^{\bu}(S) \hotimes \left[ \Omega^{0,\bu}(C, K^{1/4}_C \otimes \C^4) \oplus \Pi \Omega^{0,\bu} (C,K^{3/4}_C \otimes \C^4) \right] .
\]
The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
If we split the fields according to the direct sum above by $X, \Psi$ then the action is simply
\[
\int_{S \times C} \Psi \d_S X + \int_{S \times C} \Psi \dbar_\Sigma X .
\]
Here, we have implicitly chosen a non-degenerate symmetric pairing on $\C^4$.

@@

The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.
More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.

@@

We will assume in addition to having a THF structure that $M$ is equipped with the data of a bundle isomorphism $\wedge^{n} (\T_M \otimes \C / F)^* \cong \C$ which we will denote by~$\Omega_F$. 
If $F \cap \Bar{F} = 0$ then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.

@@

There is also the notion of the sheaf of `holomorphic vector fields' $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$. 
Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
Then we obtain a resolution
\beqn
\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
\eeqn
Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.

@@

Now we are in a place to describe a BV theory defined on an eleven-manifold $M$ equipped with a THF $F$ and a volume form $\Omega_F$ on the leaf space.
The space of fields of the theory consist of fields $\beta,\gamma, \mu, \nu$ as before but where
\beqn
\beta \in \Pi \cA_F^\bu, \quad \gamma \in \cA^{1,\bu}_F, \quad \mu \in \Pi \cA^\bu_F(\theta_F), \quad \nu \in \cA_F^\bu  .
\eeqn
Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$. 
The free part of the action functional (cf. \eqref{eqn:free}) is 
\beqn
\int_M (\gamma \thfd \mu) \Omega_F + \int_M (\beta \thfd \gamma) \Omega_F + \int_M (\beta \Div \mu) \Omega_F .
\eeqn
The interaction (cf. \eqref{eqn:int}) is
\beqn
\label{eqn:int}
\frac12 \int_{M} (\mu^2 D \gamma) \frac{\Omega_F}{1- \nu} + \frac16 \int_{M} \gamma D \gamma D \gamma .
\eeqn

>>>>

The interacting part of the action is more complicated, partly for the reason that in our presentation above it is given by a formal series in the space of fields, rather than just a polynomial in the fields. 
Explicitly, the interaction can be written as
\beqn
\label{eqn:int}
\frac12 \int_{S \times X} (\mu^2 \del \gamma) \frac{\Omega_X}{1- \nu} + \frac16 \int_{S \times X} \gamma \del \gamma \del \gamma .
\eeqn
Notice that upon varying the field $\gamma$ and assuming that $\d_{dR} \mu = 0$ and $\nu = \div \mu = 0$ we recover the equation of motion \eqref{eqn:eom2} from this action functional. 
%
%Notice that the Beltrami differential $\mu^{\Bar{i}}_j \d \zbar_{\Bar{i}} \otimes \del_z$ as well as the components of the three-form which survive the minimal twist sit inside as odd sections of this sheaf of $L_\infty$ algebras.

@@

In the works \cite{CostelloM5,CostelloM2} Costello has introduced a program to analyze holography for membranes and fivebranes in the $\Omega$-deformation of nonminimally twisted supergravity defined on multi Taub--NUT spaces.
The $\Omega$-deformation of the nonminimal twist of eleven dimensional supergravity was constructed directly from the physical theory and was argued to admit a description in terms of a holomorphic-topological gauge theory in five dimensions.
We do not recall the precise relationship between this five-dimensional theory and eleven-dimensional supergravity, but it will be helpful to recall some features of the five-dimensional theory.

@@

@@

We briefly recall the description of the minimal twist of the ABJM theory associated to the single membrane theory.
Let $K^{1/4}_C$ be a fourth-root of the canonical bundle of $C$. 
In the BV formalism, this free theory has underlying space of fields
\[
\Omega^{\bu}(S) \hotimes \left[ \Pi \Omega^{0,\bu}(C, K^{1/4}_C \otimes U) \oplus \Omega^{0,\bu} (C,K^{3/4}_C \otimes U^*) \right] 
\]
where $W\cong \C^4$ is the fundamental $\lie{sl}(4)$ representation.
The linear BRST differential is of the form $\d_{S} + \dbar_C$ where $\d_S$ is the de Rham differential along $S$ and $\dbar_C$ is the anti-holomorphic Dolbeault operator along $\Sigma$.
If we split the fields according to the direct sum above by $X, \Psi$ then the action is simply
\[
\int_{S \times C} \Psi \d_S X + \int_{S \times C} \Psi \dbar_\Sigma X .
\]
Here, we have implicitly chosen a non-degenerate symmetric pairing on $\C^4$.

@@

The eleven-dimensional model for twisted supergravity can be extended to more general geometries than products $S \times X$ where $S$ is a real one-dimensional manifold and $X$ is a Calabi--Yau fivefold.
More generally, we can define the model on an eleven-manifold $M$ equipped with a transversely holomorphic foliation (THF) equipped with the data of a non-vanishing volume form on the leaf space.
For general background on the theory of THFs we refer the reader to \cite{DuchampKalka,Rawnsley}.

@@

We will assume in addition to having a THF structure that $M$ is equipped with the data of a bundle isomorphism $\wedge^{n} (\T_M \otimes \C / F)^* \cong \C$ which we will denote by~$\Omega_F$. 
If $F \cap \Bar{F} = 0$ then $\Omega_F$ returns the usual notion of a non-vanishing holomorphic top form.
For our purposes, this is the appropriate notion of a transverse Calabi--Yau structure.

@@

There is also the notion of the sheaf of `holomorphic vector fields' $\vartheta_F$ and a sheaf of holomorphic one-forms $\Omega^1_F$ on a manifold $M$ equipped with a THF~$F$. 
Locally, on $\R^m \times \C^n$ these are vector fields of the form $f^i \del / \del z_i$ where each $f^i \in \cO_F$.
Let $\theta_F$ be the bundle $T_M \otimes \C / F$ on $M$ and declare 
$\cA^k(Q_F)$ to be the sheaf of $C^\infty$-sections of the bundle $\wedge^\bu F^k \otimes \theta_F$.
Then we obtain a resolution
\beqn
\vartheta_F \xto{\simeq} \left(\cA^\bu(\theta_F) , \thfd \otimes \id\right) .
\eeqn
The sheaf $\vartheta_F$ is equipped with a Lie bracket which extends to endow $\cA^\bu(\theta_F)$ the structure of a dg Lie algebra.

Similarly, there is a resolution for the holomorphic one-forms as $\Omega^1_F \xto{\simeq} \cA^{1,\bu}_F$ where in degree $q$ the space $\cA^{1,q}_F$ is the sheaf of $C^\infty$-sections of $\wedge^q F^* \otimes \theta_F^*$.
Similarly, we let $\cA^{p,q}_F$ be the $C^\infty$-sections $\wedge^q F^* \otimes \wedge^p \theta_F^*$.

@@

Now we are in a place to describe a BV theory defined on an eleven-manifold $M$ equipped with a THF $F$ and a volume form $\Omega_F$ on the leaf space.
The space of fields of the theory consist of fields $\beta,\gamma, \mu, \nu$ as before but where
\beqn
\beta \in \Pi \cA_F^\bu (M) , \quad \gamma \in \cA^{1,\bu}_F (M) , \quad \mu \in \Pi \cA^\bu_F(M, \theta_F), \quad \nu \in \cA_F^\bu (M)  .
\eeqn
Notice that there is a natural odd pairing between the fields $\mu, \gamma$ and $\beta, \nu$. 
The free part of the action functional (cf. \eqref{eqn:free}) is 
\beqn
\int_M (\gamma \thfd \mu) \Omega_F + \int_M (\beta \thfd \gamma) \Omega_F + \int_M (\beta \Div \mu) \Omega_F .
\eeqn
The interaction (cf. \eqref{eqn:int}) is
\beqn
\label{eqn:int}
\frac12 \int_{M} (\mu^2 D \gamma) \frac{\Omega_F}{1- \nu} + \frac16 \int_{M} \gamma D \gamma D \gamma .
\eeqn
If we assume that $\nu = \Div \mu = 0$ we recover the following equation of motion upon varying $\gamma$
\beqn
\thfd \mu + \frac12 [\mu,\mu] = D \gamma D \gamma .
\eeqn
This is a generalization of equation \eqref{eqn:eom2} for a general THF $F$ on the eleven-manifold~$M$.
